### 2021-06-18 README.Rmd
let 'er rip

>>>>

# Citing What You Do in `{peacesciencer}`

You can (and should) cite what you do in `{peacesciencer}`. The package includes a data frame of a `BibTeX` file (`ps_bib`) and a function for finding and returning `BibTeX` entries that you can include in your projects. This is the `ps_cite()` function. The `ps_cite()` function takes a string and does a partial match for relevant keywords (as `KEYWORDS`) associated with entries in the `ps_bib` file. For example, you can (and should) cite the package itself.

```{r}
ps_cite("peacesciencer")
```

You can see what are the relevant citations to consider using for the data returned by `add_democracy()`

```{r}
ps_cite("add_democracy()")
```

You can also return partial matches to see what citations are associated with, say, alliance data in this package.

```{r}
ps_cite("alliance")
```

This function might expand in complexity in future releases, but you can use it right now for finding appropriate citations. You an also scan the `ps_bib` data to see what is in there.
